---
title       : Weight Mnagement Plan
subtitle    : Course Project 
author      : Sandra Cuffee
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slide
---


## Summary

### Course Project: Weight Management Plan

#### The ui.R and server.R scripts were created to calculate how long it would take   
#### to lose up to 50 pounds by reducing caloric intake over a number of days.  In 
#### this calculator one pound is equal to 3500 calories. A reduction in 3500 
#### calories is a reduction of one pound.  The input variables pounds and calorie  
#### represent desired weight loss and daily calorie reduction.  The minimum value 
#### for pounds is five and calorie is 100. The default input values are 10 pounds 
#### and 100 for calorie. The default input values are 10 for pounds and 100 for 
#### calorie. Pounds can be incremented by five, up to the maximum of 50 and  
#### calorie can be incremented by 50, up to the maximum of 800. The days variable 
#### represents the number of days required to lose up to 50 pounds based on the 
#### pound and calorie input values and pressing the submit buttons to calculate 
#### the number of days. The default values are 10 pounds and 100 calories per day, 
#### day, would require 350 days to lose 10 pounds. 

---


```{r, echo = FALSE,warnings = FALSE}

suppressWarnings(library(shiny))
shinyUI(pageWithSidebar(
  headerPanel("Weight Loss Management Plan"),
  sidebarPanel(
    numericInput('pounds', 'Number of pounds you would like to lose up to a maximum of 50', 10, min = 5, max = 50, step= 5),
    submitButton('Submit'),
    numericInput('calorie', 'Daily calorie reduction up to a maximum of 800', 100, min = 100, max = 800, step = 50),
    submitButton('Submit')
    
  ),
  mainPanel(
    h3('Results of the plan'),
    h4('The number of pounds you want to lose is:'),
    verbatimTextOutput("inputValue1"),
    h4('The planned daily calorie reduction is:'),
    verbatimTextOutput("inputValue2"),
    h4('Which requires:'),
    verbatimTextOutput("days"),
    h4('days.')
  )
  
))

```


```{r, echo = FALSE}
  
  library(shiny)

  weightLoss <- function(pounds, calorie)
{
  x = 0   #Calorie reduction counter
  days = 0   #Number of days counter
  totalCalories = pounds * 3500 #Number of calores needed to reduce desired pounds
  while (x < totalCalories) #Calculating the number of days required
      {
          x = x + calorie
          days = days + 1
      }
  

 days #Total number of days
 
  }

shinyServer(
  function(input,input1, output, output1){
    output$inputValue1 <- renderPrint({input$pounds})
    output$inputValue2 <- renderPrint({input$calorie})
    output$days <- renderPrint({weightLoss(input$pounds,input$calorie)})
    
    
    
    
      
     
    
  }
)

```